Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-15 ms.qmd
Need to add in populations

Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r spp_wild`). Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds). Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).

>>>>

Acute and acclimation responses for wild ectotherms were much less common than studies done on captive populations ($N_{species}$ = `r spp_wild`, from XX populations). Globally, there was a clear bias towards spiecies in the Northern Hemiphere (@fig-preds). Predictions of current global changes in the opportunity for selection were generally conservative with our model explaining ~ 50% of the variation in the observed data ($R^2$ = `r round(mean(r2_2), 2)`, 95% CI: `r round(quantile(r2_2, 0.025)[1], 2)` to `r round(quantile(r2_2, 0.975)[1], 2)`).
